---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tidyverse.quiet = TRUE)
```

# siconvr

<!-- badges: start -->
  [![CRAN status](https://www.r-pkg.org/badges/version/siconvr)](https://CRAN.R-project.org/package=siconvr)
  [![R-CMD-check](https://github.com/meirelesff/siconvr/workflows/R-CMD-check/badge.svg)](https://github.com/meirelesff/siconvr/actions)
[![Codecov test coverage](https://codecov.io/gh/meirelesff/siconvr/branch/main/graph/badge.svg)](https://codecov.io/gh/meirelesff/siconvr?branch=main)
[![Travis build status](https://travis-ci.com/meirelesff/siconvr.svg?branch=main)](https://travis-ci.com/meirelesff/siconvr)
<!-- badges: end -->


`siconvr` is an R package designed to fetch and clean data on federal targeted transfers in Brazil from Plataforma +Brasil (previously SICONV). With `siconvr`, obtaining data on available policy programs maintained by the Brazilian Federal Government, proposals submitted by local governments, and NGOs to apply for such funds, among many others, takes a few seconds. 


## Installing

Install the package from using:

```{r, eval=FALSE}
install.packages("siconvr")
```


To install the package's development version, use:

```{r, eval=FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("meirelesff/siconvr")
```


Then load it with:

```{r}
library(siconvr)
```


## How to use

Using `siconvr` to fetch data from Plataforma +Brasil is easy: pass the type of data you want to the `get_siconv` function and you are ready to go. Here's an example:


```{r, eval=FALSE}
progs <- get_siconv("programas")
```

### Available datasets

Here a list of available datasets one can fetch using `siconvr`:

```{r echo=FALSE, message=TRUE, warning=FALSE}
library(tidyverse)

tribble(
  
  ~Option, ~Data,
  "`programas`", "data on available programs maintained by the Federal Government",
  "`programas_propostas`",  "keys to match programs and proposals submited to the Federal Government",
  "`propostas`",  "data on proposals submited to the Federal Government",
  "`convenios`",  "data on proposals effectivelly signed by the Federal Governments",
  "`emendas`",  "data on amendments to the the federal budget made by Brazilian Federal Deputies and Senators to fund federal transfers",
  "`planos`",  "data on application plans submited to the Federal Government",
  "`empenhos`",  "data on transfers appropriated in the Federal Budget",
  "`desembolsos`",  "data on transfers disbursements by the Federal Government",
  "`obtv`",  "data on payments made to local suppliers and contractors hired to execute funded projects",
  "`historico`",  "proposals' track record",
  "`ingresso_contrapartida`",  "record of counterpart payments",
  "`aditivos`",  "data on contracts' budget addendums",
  "`crono_metas`",  "cronogram of project's goals",
  "`cronogramas`",  "project's execution cronograms",
  "`consorcios`",  "data on proposals where multiple local governments or private entities cooperate to request federal resources",
  "`empenhos_desembolsos`",  "keys to match appropriations and disbursements by Federal Government",
  "`proponentes`",  "data on proposals' proponents",
  "`cronograma_desembolsos`",  "cronogram of project's transfers disbursements",
  "`justificativas`", "proposals' justifications"
) %>%
  knitr::kable()
```


### Options

By default, `get_siconv` tries to read fetched data using `UTF-8` encoding. In case this does not work for you, use the argument `encoding` to change that:

```{r, eval=FALSE}
emp <- get_siconv("empenhos", encoding = "latin-1")
```


To save Plataforma +Brasil server resources, `get_siconv` stores a cache of fetched data in a folder in working directory named `cache` -- so you don't need to download the same data again. To avoid cacheing date, set `cache` to `FALSE`:

```{r, eval=FALSE}
obtv <- get_siconv("obtv", cache = FALSE)
```

Finally, one might also want to avoid `get_siconv`'s messages when fetching data. This can be done with:

```{r, eval=FALSE}
historico <- get_siconv("historico", verbose = FALSE)
```



## Contributions

We welcome suggestions to improve `siconvr`. In case you wish to contribute with code, feel free to push commits to this repository -- we will be more than happy to acknowledge any assistance by updating our contributors' list.


## Authors


[Fernando Meireles](https://fmeireles.com) e [Marcus Vinícius de Sá Torres](http://marcustorresz.github.io/)


